Composing like a human

### 2019-04-29 paper/main.tex
should-be-mandatory backup

\newcommand{\hsp}{\hspace{10pt}}
\titleformat{\chapter}[hang]{\Huge\bfseries}{\textcolor{base02}{\thechapter \hsp \vline}\hsp}{0pt}{\Huge\bfseries}
\titleformat{\section}[hang]{\Large\bfseries}{\textcolor{base01}{\thesection \hsp \vline}\hsp}{0pt}{\Large\bfseries}
\titleformat{\subsection}[hang]{\large\bfseries}{\textcolor{base01}{\thesubsection \hsp \vline}\hsp}{0pt}{\large\bfseries}

@@

@@

\section{"Just... One more bite"}\label{sec:hungry}

@@

>>>>

\newcommand{\hsp}{\hspace{10pt}}
\titleformat{\chapter}[hang]{\Huge\bfseries}{\textcolor{base02}{\thechapter }\hsp}{0pt}{\Huge\bfseries}
\titleformat{\section}[hang]{\Large\bfseries}{\textcolor{base01}{\thesection}\hsp}{0pt}{\Large\bfseries}
\titleformat{\subsection}[hang]{\large\bfseries}{\textcolor{base01}{\thesubsection}\hsp}{0pt}{\large\bfseries}

@@

% Drawings
\usepackage{tikz}
\usetikzlibrary{arrows.meta, fit, positioning}

\tikzset{
    neuron/.style={
        circle, draw, thick,
        inner sep=0pt,
        minimum size=3.0em,
        node distance=4em
    },
    io/.style={
        neuron,
        fill=base01
    },
    conn/.style={
        thick,
        -{Straight Barb[angle=60:2pt 3]},
    }
}

@@

\section{We always want more}\label{sec:hungry}

@@

This chapter takes a deep-dive into the fields of meta-learning and generative networks in order to highlight their current state of affairs. This will lay the groundwork for the experiments detailed in Chapter \ref{chap:methods}. Section \ref{sec:lstm} will present the principal network architecture of this paper, the Long Short-Term Memory network, and argument for its use as the foundation of a generative network. Section \ref{sec:generative} will introduce Generative Adversarial Networks, a training method build specifically for the task, whereas Section \ref{sec:learn2learn} will formally introduce meta-learning, several approaches to it, and finally narrow down to current state-of-the-art algorithms.

\section{Long Short-Term Memory Networks} \label{sec:lstm}

In a standard ANN, the data traverses the network through the input layer, to the hidden layer, and finally reaching the output layer; setup which is generally known as a feedforward neural network \parencite[Figure \ref{fig:feedforward_net};][]{graves_supervised_2012}. Broadly, this type of network is defined by the fact that its connections do not form cycles. If however we relax this condition, we arrive at a recurrent neural network \parencite[Figure \ref{fig:rnn_folded};][]{rumelhart_learning_1986}: a family of neural networks specifically designed for processing sequential data \parencite{goodfellow_deep_2016}.

Concretely, information passes through the RNN similarly to the feedforward network except that the activations which arrive at the hidden layer are from the current external input and prior hidden activations from the previous timestep \parencite{graves_supervised_2012}. Thus a formal definition of the network would be represented by

\begin{equation}
    h^t = f(h^{t-1}; x^t; \theta)
\end{equation}

where $h^t$ is the state of the hidden layer at time $t$, $x^t$ is the input at time $t$, and $\theta$ the bias.

\begin{figure}[t]
    \centering
    \begin{tikzpicture}
        \node[io] (x1) {$x_1$};
        \node[io, above=4em of x1] (x2) {$x_2$};
        \node[io, above=4em of x2] (x3) {$x_3$};

        \node[neuron, right= of x1] (h1) {$h_1$};
        \node[neuron, above=4em of h1] (h2) {$h_2$};
        \node[neuron, above=4em of h2] (h3) {$h_3$};

        \node[io, right= of h2] (y) {$y$};

        \foreach \x in {1, 2, 3}
            \foreach \h in {1, 2, 3}
                \draw[conn] (x\x) -- (h\h);

        \foreach \h in {1, 2, 3}
            \draw[conn] (h\h) -- (y);
    \end{tikzpicture}
    \caption{Example of a feedforward neural network with three nodes in the input layer ($x_1$, $x_2$, $x_3$), three nodes in the hidden layer ($h_1$, $h_2$, $h_3$), and an output layer a single node ($y$).}
    \label{fig:feedforward_net}
\end{figure}

\begin{figure}[ht]
    \centering
    \begin{subfigure}{.24\linewidth}
        \begin{tikzpicture}
            [align=center]
            % Draw recurrent network
            \node[neuron] (h) {$h$};
            \node[io, below=4em of h] (x) {$x$};
            \node[io, above=4em of h] (y) {$y$};

            \draw[conn] (h) -- node [left=0.5em, midway, align=center] {$V$} (y);
            \draw[conn] (x) -- node [left=0.5em, midway, align=center] {$U$} (h);
            \draw[conn] (h.north) to [out=150, in=180, loop, looseness=4] node[left=0.5em, midway, align=center] {$W$} (h.west);

        \end{tikzpicture}
        \caption{Folded}
        \label{fig:rnn_folded}
    \end{subfigure}
    \begin{subfigure}{.74\linewidth}
        \begin{tikzpicture}
            [align=center]
            % Draw middle unfold
            \node[neuron] (ht) {$h^t$};
            \node[io, below=4em of ht] (xt) {$x^t$};
            \node[io, above=4em of ht] (yt) {$y^t$};

            \draw[conn] (ht) -- node [left=0.5em, midway, align=center] {$V$} (yt);
            \draw[conn] (xt) -- node [left=0.5em, midway, align=center] {$U$} (ht);

            % Draw left unfold
            \node[neuron, left = of ht] (ht-1) {$h^{t-1}$};
            \node[io, below=4em of ht-1] (xt-1) {$x^{t-1}$};
            \node[io, above=4em of ht-1] (yt-1) {$y^{t-1}$};

            \node[left= of ht-1] (nullLeft) {};

            \draw[conn] (ht-1) -- node [left=0.5em, midway, align=center] {$V$} (yt-1);
            \draw[conn] (xt-1) -- node [left=0.5em, midway, align=center] {$U$} (ht-1);

            \draw[conn] (ht-1) -- node [above=0.5em, midway, align=center] {$W$} (ht);
            \draw[conn] (nullLeft) -- node [above=0.5em, midway, align=center] {$W$} (ht-1);
            % Draw right unfold
            \node[neuron, right= of ht] (ht+1) {$h^{t+1}$};
            \node[io, below=4em of ht+1] (xt+1) {$x^{t+1}$};
            \node[io, above=4em of ht+1] (yt+1) {$y^{t+1}$};

            \node[right= of ht+1] (nullRight) {};

            \draw[conn] (ht+1) -- node [left=0.5em, midway, align=center] {$V$} (yt+1);
            \draw[conn] (xt+1) -- node [left=0.5em, midway, align=center] {$U$} (ht+1);

            \draw[conn] (ht) -- node [above=0.5em, midway, align=center] {$W$} (ht+1);
            \draw[conn] (ht+1) -- node [above=0.5em, midway, align=center] {$W$} (nullRight);

        \end{tikzpicture}
        \caption{Unfolded}
        \label{fig:rnn_unfolded}
    \end{subfigure}
\end{figure}

\section{Generative Adversarial Networks} \label{sec:generative}

\section{Learning to learn} \label{sec:learn2learn}
